MS_CNuptake.Rmd

### 2022-08-30 MS_CNuptake.Rmd
tiny update

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("~/data/output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
```

>>>>

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/newphy_figs7.jpg",sep=""),width = 22, height = 10)
```
